---
title: "LIRE Dis Manibus formula"
author: "Petra Hermankova"
date: "9/24/2021"
output: html_document
---


```{r setup, echo=TRUE, message=FALSE}
library(tidyverse)
#library(sdam)
library(jsonlite)
library(dplyr)
library(reticulate)
library(sf)
library(leaflet)
```

```{r}
use_condaenv("RStudio") # Use this to use a conda environment
#use_python("/usr/local/bin/python")
```

```{python}
import geopandas as gpd # https://vincent.doba.fr/posts/20210407_install-fiona-on-windows/ & https://geopandas.org/getting_started/install.html Issues with geopandas on windows. The requirements.txt file might be able to install the packages, if not you should look into these geopandas links.
import requests
import seaborn as sns
import matplotlib.colors as mcolors
import matplotlib.pyplot as plt
from scipy.stats import trapz
import scipy
#import nltk
import json
import tempun
#import sddk
import numpy as np
import pandas as pd
pd.options.display.max_columns = 1000  # to see all columns
```

```{r}
LIRE<- sf::st_read("https://zenodo.org/record/5074774/files/LIREg.geojson?download=1")
```


## Text preparation

Converting the text of inscriptions to lowercase
```{r}
LIRE <- LIRE %>% 
  mutate(clean_text_interpretive_word_lowercase = str_to_lower(LIRE$clean_text_interpretive_word))
```

# Dis Manibus epigraphic formula in space and time

Typically occurs on funerary inscriptions, invocation of the underworld gods.

Canonic Versions:

D M
D M S
Dis Manibus
Diis Manibus
Dis Manibus Sacrum
Diis Manibus Sacrum

## Searching for all *typical* variants of the formula

```{r}
dis_manibus_regex <- "\\bd m s\\b|\\bd m\\b|di{1,2}s manibus sacrum|di{1,2}s manibus"

dis_manibus<- str_subset(LIRE$clean_text_interpretive_word_lowercase, dis_manibus_regex)

# separating them in a new attribute
LIRE<- LIRE %>% 
  mutate(form_dis_manibus = str_extract(LIRE$clean_text_interpretive_word_lowercase, dis_manibus_regex))

# overview
table(str_extract(LIRE$clean_text_interpretive_word_lowercase, dis_manibus_regex))
```

```{r}
# capturing context - 5 words before the formula and 5 words after the formula
LIRE<- LIRE %>% 
  mutate(dis_manibus_in_context_10w = str_extract(LIRE$clean_text_interpretive_word_lowercase, "(\\w*\\s){0,6}\\bd m s\\b|\\bd m\\b|di{1,2}s manibus sacrum|di{1,2}s manibus(\\w*\\s){0,6}")) 
```

Subsetting dataset to contain only records with formula
```{r}
#non-empty dis manibus attribute
LIRE_DM <- LIRE %>% 
  filter(!is.na(form_dis_manibus))
```


## Type of formula by province - cummulative
```{r, fig.height=10}
LIRE_DM %>% 
  #count(province_label_clean, form_dis_manibus, sort=T) %>% 
  ggplot(aes(y=province_label_clean)) + 
  geom_bar(aes(fill=form_dis_manibus)) +
  #coord_cartesian(xlim=c(0,1700)) +
  theme_minimal() +
  theme(text = element_text(size=12)) +
  labs(y="Roman province", x="Formula", title= "Dis Manibus formula by province", subtitle = ggtitle(paste("n =", nrow(LIRE_DM), "inscriptions (LIRE)"))) 
  #geom_label(aes(label= form_dis_manibus)) +
  #geom_label(aes(label = form_dis_manibus), colour = "black", fontface = "bold", hjust = -0.1) 
```


## Map of Dis Manibus occurences - cummulative
```{r}
# preparation of subsets
# dis manibus formula
LIRE_dis_manibus <- LIRE_DM %>% 
  filter(form_dis_manibus == "dis manibus")

# diis manibus formula
LIRE_diis_manibus <- LIRE_DM %>% 
  filter(form_dis_manibus == "diis manibus")

# dis manibus sacrum formula
LIRE_dis_manibus_sacrum <- LIRE_DM %>% 
  filter(form_dis_manibus == "dis manibus sacrum")

# diis manibus sacrum formula
LIRE_diis_manibus_sacrum <- LIRE_DM %>% 
  filter(form_dis_manibus == "diis manibus sacrum")

#abbreviated dis manibus formula
LIRE_d_m <- LIRE_DM %>% 
  filter(form_dis_manibus == "d m")

#abbreviated dis manibus sacrum formula
LIRE_d_m_s <- LIRE_DM %>% 
  filter(form_dis_manibus == "d m s")
```


```{r}
DM_map<- #head(LIRE_DM, 100) %>% 
  leaflet(LIRE_DM) %>% 
  leaflet(width="100%") %>%
  #addProviderTiles("Stamen.Watercolor")%>% # Add CartoDB map tiles
  addProviderTiles("Stamen.TerrainBackground")%>% # Add CartoDB map tiles
  #addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  #addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>%
  setView( lng = 12.9239625, lat = 41.9515694, zoom = 3.5 ) %>%
  #setMaxBounds(lat1=43.633977, lng1 =-11.227926 , lat2=35.133882 , lng2=50.882336) %>%
  #addPolylines(data = roads, color = "purple", weight = 1, opacity = 0.7) %>% 
  
  addCircles(lng = LIRE_dis_manibus$Longitude, 
             lat = LIRE_dis_manibus$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "blue" , fillColor = "blue",) %>%
  addCircles(lng = LIRE_dis_manibus_sacrum$Longitude, 
             lat = LIRE_dis_manibus_sacrum$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "red" , fillColor = "red",) %>%
    addCircles(lng = LIRE_diis_manibus$Longitude, 
             lat = LIRE_diis_manibus$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "black" , fillColor = "black",) %>%
  addCircles(lng = LIRE_diis_manibus_sacrum$Longitude, 
             lat = LIRE_diis_manibus_sacrum$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "orange" , fillColor = "orange",) %>%
  addCircles(lng = LIRE_d_m_s$Longitude, 
             lat = LIRE_d_m_s$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "yellow" , fillColor = "yellow",)  %>% 
  addCircles(lng = LIRE_d_m$Longitude, 
             lat = LIRE_d_m$Latitude, opacity = 0.3, radius = 0.5, fill = T , color = "green" , fillColor = "green",) %>% 

  #addAwesomeMarkers(~LIRE$longitude, ~LIRE$latitude, icon=icons) %>% 
  addLegend(position = "bottomright",
  colors = c("Blue", "Black", "Green", "Red", "Orange", "Yellow"),
  labels = c("dis manibus", "diis manibus", "d m", "dis manibus sacrum", "diis manibus sacrum", "d m s"), opacity = 1,
  title = "Dis Manibus formula (LIRE)" ) %>% 
  addScaleBar(position="bottomleft")

DM_map
```


## Dis manibus formula preferences

Preparation of the dataset - unique people records

```{r}
LIRE_people<- LIRE_DM %>% 
  unnest(people)
nrow(LIRE_people)
```



### Formula by gender of person on inscription
```{r}
LIRE_people %>% 
  #filter(form_dis_manibus == "dis manibus" | form_dis_manibus == "dis manibus sacrum") %>% 
  mutate(gender_clean = str_replace_all(gender, "W\\?", "female")) %>%
  mutate(gender_clean = str_replace_all(gender_clean, "M\\?", "male")) %>%
  count(gender_clean, form_dis_manibus, sort=T) %>% 
  mutate(freq = n/(sum(n)/100)) %>% 
  ggplot(aes(y=gender_clean, x=n)) +
  geom_col(aes(fill=form_dis_manibus)) +
  #geom_label(aes(label = round(freq, 2)), hjust=0.3, size = 3.5) +
  theme_linedraw(base_size = 12) +
  labs(y="Gender", x="Formula", title= "Dis Manibus formula by gender", subtitle = ggtitle(paste("n =", length(LIRE_DM$people), "inscriptions (LIRE)"))) 


```

### Formula by status of person on inscription
```{r, fig.width=14, fig.height=10}

LIRE_people %>% 
  #filter(form_dis_manibus == "dis manibus" | form_dis_manibus == "dis manibus sacrum") %>% 
  mutate(status_clean = str_replace_all(status, "\\?", "")) %>% 
  count(status_clean, form_dis_manibus, sort=T) %>% 
  ggplot(aes(y=status_clean, x=n)) +
  geom_col(aes(fill=form_dis_manibus)) +
  #coord_cartesian(xlim = c(0, 15800)) +
  labs(y="Status", x="Individuals", title= "Dis Manibus formula by personal status", subtitle = ggtitle(paste("n =", nrow(LIRE_people), "individuals (LIRE)"))) +
  theme(legend.position = c(0.9, 0.15)) +
  scale_fill_discrete(name="Formula")
```

### Formula by age of person on inscription
```{r}
LIRE_people %>% 
  mutate(age_yr = as.numeric(`age: years`)) %>% 
  filter(!is.na(age_yr)) %>% 
  count(age_yr, form_dis_manibus, sort=T) %>% 
  ggplot(aes(age_yr, n)) +
  geom_point(aes(colour=form_dis_manibus)) +
  labs(y="Individuals", x="Years at death", title= "Dis Manibus formula by age of the deceased", subtitle = ggtitle(paste("n =", nrow(LIRE_people), "individuals (LIRE)")))
  
  
```

### Formula by type of inscribed monument
```{r}
LIRE_DM %>% 
  count(type_of_monument_clean, form_dis_manibus, sort = T) %>% 
  ggplot(aes(y=type_of_monument_clean, x=n)) + 
  geom_col(aes(fill=form_dis_manibus)) +
  theme_minimal() +
  labs(y="Inscribed object", x="Inscriptions", title= "Dis Manibus formula by inscribed object", subtitle = ggtitle(paste("n =", nrow(LIRE_DM), "inscriptions (LIRE)")))
```

### Formula by type of inscribed material
```{r}
LIRE_DM %>% 
  count(material_clean, form_dis_manibus, sort = T) %>% 
  ggplot(aes(y=material_clean, x=n)) + 
  geom_col(aes(fill=form_dis_manibus)) +
  theme_minimal() +
  labs(y="Inscribed material", x="Inscriptions", title= "Dis Manibus formula by inscribed material", subtitle = ggtitle(paste("n =", nrow(LIRE_DM), "inscriptions (LIRE)")))
```

# Temporal usage of the formulae


```{r}
# preparation of the dataset
LIRE_DM$not_before <- as.numeric(as.character(LIRE_DM$not_before))
LIRE_DM$not_after <- as.numeric(as.character(LIRE_DM$not_after))
```


```{r}
LIRE_mini <- LIRE %>% 
  select(not_after, not_before, clean_text_interpretive_word, clean_text_interpretive_word_lowercase, form_dis_manibus, type_of_inscription_auto, Latitude, Longitude)
```

```{r}
# How many inscriptions have both dates?
LIRE_dated_mini <- LIRE_mini %>% 
  filter(not_before != "NaN" & not_after != "NaN")
```

```{python}
LIRE_dated = r.LIRE_dated_mini
len(LIRE_dated)
```

```{python}
# Generate a list of 1000 random dates for each inscription in the dataset
LIRE_dated["random_dates"] = LIRE_dated.apply(lambda row: tempun.model_date(
    row["not_before"], row["not_after"], size=1000,), axis=1)
```

```{r}
# saving as r-object
py$LIRE_dated -> LIRE_dated_mini_sim
```



```{python}
# Count random dates in temporal timeblocks in a specified time range (from 200 BC to 600 AD, temporal blocks by 25 years)
LIRE_complete_simulations = tempun.timeblocks_from_randoms(
    LIRE_dated, "random_dates", [-200, 600, 25])
```

```{python}
LIRE_complete_simulations[1:2]
```


```{python}
# Figure 1
# plot all the dataset to see the epigraphic production in time
plt.style.use("seaborn-white")
plt.rcParams['figure.dpi'] = 300
plt.rcParams['font.size'] = 10
tab_colors_list = list(mcolors.TABLEAU_COLORS.keys())
fig, ax = plt.subplots(figsize=(14, 6), tight_layout=True)
tempun.plot_timeblocks_data(
    LIRE_complete_simulations, ax=ax, color="blue", label=f"LIRE (n={len(LIRE_dated)})")
    
ax.set_xlabel("Year", weight="bold")
ax.set_ylabel("Count", weight="bold")
ax.set_title("Total epigraphic production over time (LIRE)")
ax.legend(title="Data source", title_fontsize="large", bbox_to_anchor=(1, 1), loc='upper right')
#plt.axvline(x=212, linewidth=0.5, color = 'orange', linestyle='dashed')
#fig.suptitle(f'Comparison of epigraphic production over time', fontsize=16,fontweight="bold")
#plt.savefig('../Fig1_Epi_production_time.png')
fig
```


```{python}
# Inscriptions by their type over time, LIRE
simulations_by_type_len_LIRE = []
for ins_type in r.LIRE_dated["form_dis_manibus"].unique():
    if ins_type != "NULL":
        subset_df = LIRE_dated[LIRE_dated["form_dis_manibus"] == ins_type]
        simulations_by_type_len_LIRE.append((ins_type, len(subset_df)))
simulations_by_type_len_LIRE = sorted(
    simulations_by_type_len_LIRE, key=lambda x: x[1], reverse=True)
simulations_by_type_len_LIRE
simulations_by_type_LIRE = []
for ins_type_tup in simulations_by_type_len_LIRE[:8]:
    subset_df = LIRE_dated[LIRE_dated["form_dis_manibus"]
                          == ins_type_tup[0]]
    simulations = tempun.timeblocks_from_randoms(
        subset_df, "random_dates", [-200, 600, 25])
    ins_type_N = len(subset_df)
    simulations_by_type_LIRE.append([ins_type_tup[0], ins_type_N, simulations])
simulations_by_type_LIRE = sorted(
    simulations_by_type_LIRE, key=lambda x: x[1], reverse=True)
date_vars_by_instypes = []
for ins_type_tup in simulations_by_type_len_LIRE[:10]:
    subset_df = LIRE_dated[LIRE_dated["form_dis_manibus"]
                          == ins_type_tup[0]]
    date_vars = []
    for n in range(100):
        date_vars.append(
            [date_var[n] for date_var in subset_df["random_dates"] if date_var != None])
    date_vars_by_instypes.append(date_vars)
```

```{python}
simulations_by_type_len_LIRE
```

```{python}
# Figure 2
plt.style.use("seaborn-white")
plt.rcParams['figure.dpi'] = 300
plt.rcParams['font.size'] = 10
fig, [ax1, ax2] = plt.subplots(2, 1, figsize=(14, 12), tight_layout=True)
for ins_type_sims, color in zip(simulations_by_type_LIRE, tab_colors_list[:len(simulations_by_type_LIRE)]):
    tempun.plot_timeblocks_data(ins_type_sims[2], ax=ax1, color=color)
ax1.set_xlabel("Year", weight="bold")
ax1.set_ylabel("Count", weight="bold")
ax1.set_title(f"`Dis manibus` formula on inscriptions over time (LIRE, n={len(LIRE_dated)})", weight="bold")
markers = [plt.Line2D([0, 0], [0, 0], color=color, lw=4)
           for color in tab_colors_list[:len(simulations_by_type_LIRE)]]
legend_labels_LIRE = [tup[0] + " (n={})".format(str(tup[1])) for tup in simulations_by_type_LIRE]
ax1.legend(markers, legend_labels_LIRE, numpoints=1,  
           title=f"Formula types (LIRE n={len(LIRE_dated)})", title_fontsize="large", bbox_to_anchor=(1, 1), loc='upper right')
#plt.savefig('../Fig2_Typologies_comparison_time.png')
fig
```



## Periods 
```{python}
# periods definitions
periods = {  # to avoid overlaps, startdates are postponed by one year, when needed
    "Late Roman Republic": {"startdate": -200, "enddate": -26, "duration": 175},
    "Julio-Claudian dyn.": {"startdate": -27, "enddate": 68, "duration": 95},
    "Flavian dyn.": {"startdate": 69, "enddate": 96,"duration": 28},
    "Nerva-Antonine dyn.": {"startdate": 97, "enddate": 192, "duration": 96},
    "Severan dyn.": {"startdate": 193, "enddate": 235, "duration": 43},
    "Military emperors": {"startdate": 236, "enddate": 284,"duration": 49},
    "Tetrarchy-Constantine I": {"startdate": 285, "enddate": 337,"duration": 53},
    "Late Roman Empire": {"startdate": 338, "enddate": 600,"duration": 263}
}
timeblocks_periods = [(periods[period]["startdate"],
                       periods[period]["enddate"],
                       periods[period]["duration"]) for period in periods]
timeblocks_periods
```

```{python}
# periods definitions
periods = {  # to avoid overlaps, startdates are postponed by one year, when needed
    "First c. AD": {"startdate": 1, "enddate": 100, "duration": 100},
    "Second c. AD": {"startdate": 101, "enddate": 200, "duration": 100},
    "Third c. AD": {"startdate": 201, "enddate": 300,"duration": 100}
}
timeblocks_periods = [(periods[period]["startdate"],
                       periods[period]["enddate"],
                       periods[period]["duration"]) for period in periods]
timeblocks_periods
```


```{python}
def date_to_str(date):
    if date < 0:
        date = str(abs(date)) + " BC"
    else:
        date = "AD " + str(date)
    return date
periods_labels = []
for period in periods.keys():
    start = date_to_str(periods[period]["startdate"])
    end = date_to_str(periods[period]["enddate"])
    periods_labels.append(period + "\n({0}-{1})".format(start, end))
periods_labels
```

```{python}
# loading shapefile from Pleaides for the largest extent of the Roman Empire, AD 117
# source: https://raw.githubusercontent.com/pelagios/magis-pleiades-regions/main/pleiades-regions-magis-pelagios.geojson
pleiades_regions = gpd.read_file('https://raw.githubusercontent.com/pelagios/magis-pleiades-regions/main/pleiades-regions-magis-pelagios.geojson', driver='GeoJSON')
RE_merged = pleiades_regions.unary_union
```

```{python}
def get_date_var(randoms):
    try:
        return randoms[0]
    except:
        return None
# selecting one random date out of the 1000 version
LIRE_dated["date_var_1"] = LIRE_dated["random_dates"].apply(get_date_var)
```

```{r}
# updating the values in existing r-object
py$LIRE_dated -> LIRE_dated
```

```{python}
# modifying coordinates in LIRE to fit the script
# LIRE_dated[['Longitude', 'Latitude']] = pd.DataFrame(LIRE_dated.coordinates. tolist(), index=LIRE_dated.index)
```

```{python}
LIRE_dated_df_by_periods = []
for period in timeblocks_periods:
    LIRE_dated_sample = LIRE_dated[LIRE_dated["date_var_1"].between(
        period[0], period[1])]
    # tranforming LIRE as geodataframe
    LIRE_dated_sample = LIRE_dated_sample[LIRE_dated_sample["Latitude"].notnull()]
    LIRE_dated_sample = gpd.GeoDataFrame(LIRE_dated_sample, geometry=gpd.points_from_xy(LIRE_dated_sample["Longitude"], LIRE_dated_sample["Latitude"]))
    # selecting only those dated and within borders of the Empire (the largest extent in AD 117)
    LIRE_dated_sample = LIRE_dated_sample[LIRE_dated_sample.within(RE_merged)]
    LIRE_dated_df_by_periods.append(LIRE_dated_sample)
```

```{python}
# Figure 3
# plot LIRE inscriptions with location in 8 plots grouped by period
plt.style.use("seaborn-white")
plt.rcParams['figure.dpi'] = 300
plt.rcParams['font.size'] = 10
fig, axs  = plt.subplots(4, 2, figsize=(7, 7), tight_layout=True)
contexts_pct = {}
    
for df_LIRE, ax, period in zip(LIRE_dated_df_by_periods, axs.ravel(), periods_labels):
    pleiades_regions.plot(ax=ax, color="lightgray")
    df_LIRE.plot(markersize=0.04, color="darkblue", ax=ax, alpha=0.2, label=len(df_LIRE))
    ax.set_title(period, fontsize=6)
    ax.set_axis_off()
    markers = [plt.Line2D([0,0],[0,0],color=color, marker=".", linestyle="") for color in ["darkblue", "red"]]
    legend_labels = ["LIRE (n={0})".format(str(len(df_LIRE)))]
    
    ax.legend(markers, legend_labels, numpoints=1, bbox_to_anchor=(0.6, 1), loc='upper left', fontsize=5)
   
plt.tight_layout(pad=0)
plt.subplots_adjust(wspace=0.0, hspace=0.0)
#fig.suptitle(f'Spatial extent of the epigraphic production by historic period', fontsize=8, fontweight="bold")
#plt.savefig('../figures/Fig3_Formulae_production_periods.png')
fig
```

# Combined two most common types as time slices

```{python}
dis_manibus = LIRE_dated[LIRE_dated["form_dis_manibus"] == "dis manibus"]
len(dis_manibus)
```
```{python}
diis_manibus = LIRE_dated[LIRE_dated["form_dis_manibus"] == "diis manibus"]
len(diis_manibus)
```

```{python}
dis_manibus_sac = LIRE_dated[LIRE_dated["form_dis_manibus"] == "dis manibus sacrum"]
len(dis_manibus_sac)
```
```{python}
diis_manibus_sac = LIRE_dated[LIRE_dated["form_dis_manibus"] == "diis manibus sacrum"]
len(diis_manibus_sac)
```



```{python}
LIRE_dated_df_by_periods_dm = []
for period in timeblocks_periods:
    LIRE_dated_sample_dm = dis_manibus[dis_manibus["date_var_1"].between(
        period[0], period[1])]
    # transforming LIRE as geodataframe
    LIRE_dated_sample_dm = LIRE_dated_sample_dm[LIRE_dated_sample_dm["Latitude"].notnull()]
    LIRE_dated_sample_dm = gpd.GeoDataFrame(LIRE_dated_sample_dm, geometry=gpd.points_from_xy(LIRE_dated_sample_dm["Longitude"], LIRE_dated_sample_dm["Latitude"]))
    # selecting only those dated and within borders of the Empire (the largest extent in AD 117)
    LIRE_dated_sample_dm = LIRE_dated_sample_dm[LIRE_dated_sample_dm.within(RE_merged)]
    LIRE_dated_df_by_periods_dm.append(LIRE_dated_sample_dm)
```

```{python}
LIRE_dated_df_by_periods_dm
```


```{python}
LIRE_dated_df_by_periods_dms = []
for period in timeblocks_periods:
    LIRE_dated_sample_dms = dis_manibus_sac[dis_manibus_sac["date_var_1"].between(
        period[0], period[1])]
    # transforming LIRE as geodataframe
    LIRE_dated_sample_dms = LIRE_dated_sample_dms[LIRE_dated_sample_dms["Latitude"].notnull()]
    LIRE_dated_sample_dms = gpd.GeoDataFrame(LIRE_dated_sample_dms, geometry=gpd.points_from_xy(LIRE_dated_sample_dms["Longitude"], LIRE_dated_sample_dms["Latitude"]))
    # selecting only those dated and within borders of the Empire (the largest extent in AD 117)
    LIRE_dated_sample_dms = LIRE_dated_sample_dms[LIRE_dated_sample_dms.within(RE_merged)]
    LIRE_dated_df_by_periods_dms.append(LIRE_dated_sample_dms)
```

```{python}
LIRE_dated_df_by_periods_dms
```


```{python}
# Figure 4
# plot LIRE inscriptions with location in 8 plots grouped by period
plt.style.use("seaborn-white")
plt.rcParams['figure.dpi'] = 300
plt.rcParams['font.size'] = 12
#fig, axs  = plt.subplots(4, 2, figsize=(7, 7), tight_layout=True)
fig, axs  = plt.subplots(3, 1, figsize=(10, 10), tight_layout=True)
contexts_pct = {}
    
for df_LIRE_DMs, df_LIRE_DM, ax, period in zip(LIRE_dated_df_by_periods_dms, LIRE_dated_df_by_periods_dm, axs.ravel(), periods_labels):
    pleiades_regions.plot(ax=ax, color="lightgray")
    df_LIRE_DM.plot(markersize=0.04, color="darkblue", ax=ax, alpha=0.3, label=len(df_LIRE_DMs))
    df_LIRE_DMs.plot(markersize=0.04, color="red", ax=ax, alpha=0.3, label=len(df_LIRE_DM))
    ax.set_title(period, fontsize=6)
    ax.set_axis_off()
    markers = [plt.Line2D([0,0],[0,0],color=color, marker=".", linestyle="") for color in ["darkblue", "red"]]
    legend_labels = ["dis manibus (n={0})".format(str(len(df_LIRE_DM))), 
                     "dis manibus sacrum (n={0})".format(str(len(df_LIRE_DMs)))]
    
    ax.legend(markers, legend_labels, numpoints=1, bbox_to_anchor=(0.6, 1), loc='upper left', fontsize=5)
   
plt.tight_layout(pad=0)
plt.subplots_adjust(wspace=0.0, hspace=0.0)
fig.suptitle(f'Spatial distribution of "dis manibus" formula in the first three centuries AD (LIRE dataset)', fontsize=8, fontweight="bold")
#plt.savefig('Fig4_Formulae_compared_production_periods.png')
plt.savefig('Fig4_Formulae_compared_production_century.png')
fig
```



# Creating three snaphots in time

From simulated dates take 1-100, 101-200, 201-300 and then create a network.

```{r}
LIRE_dated[80]
```

```{r}
LIRE_1CAD<- LIRE_dated %>% 
  filter(date_var_1 > 0 & date_var_1 < 101) 

LIRE_2CAD<- LIRE_dated %>% 
  filter(date_var_1 > 100 & date_var_1 < 201)

LIRE_3CAD<- LIRE_dated %>% 
  filter(date_var_1 > 200 & date_var_1 < 301)
```


# Clustering of formulae in three time slices

```{r, 1CAD}
# Damerau-Levenshtein method - allows for substitution, deletion, insertion and transposition of individual characters

dl_distance_1CAD<- stringdistmatrix(LIRE_1CAD$form_dis_manibus, LIRE_1CAD$form_dis_manibus, method= "dl")
table(dl_distance_1CAD)
dl_distance_1CAD


# renaming rows and columns
idnames <- unique(as.character(LIRE_1CAD$id))
rownames(dl_distance_1CAD) <- idnames
colnames(dl_distance_1CAD) <- idnames

# Clustering the distance results in a dendrogram
hc_1CAD <- hclust(as.dist(dl_distance_1CAD), method = "complete")

plot(hc_1CAD, main ="Clustering of 'Dis Manibus' inscriptions in the 1st c. AD", xlab="Clusters")
rect.hclust(hc_1CAD, k=3)

```

```{r, 2CAD}
# Damerau-Levenshtein method - allows for substitution, deletion, insertion and transposition of individual characters

dl_distance_2CAD<- stringdistmatrix(LIRE_2CAD$form_dis_manibus, LIRE_2CAD$form_dis_manibus, method= "dl")
table(dl_distance_2CAD)
dl_distance_2CAD


# renaming rows and columns
idnames <- unique(as.character(LIRE_2CAD$id))
rownames(dl_distance_2CAD) <- idnames
colnames(dl_distance_2CAD) <- idnames

# Clustering the distance results in a dendrogram
hc_2CAD <- hclust(as.dist(dl_distance_2CAD), method = "complete")

plot(hc_2CAD, main ="Clustering of 'Dis Manibus' inscriptions in the 2nd c. AD", xlab="Clusters")
rect.hclust(hc_2CAD, k=3)
```

```{r, 3CAD}
# Damerau-Levenshtein method - allows for substitution, deletion, insertion and transposition of individual characters

dl_distance_3CAD<- stringdistmatrix(LIRE_3CAD$form_dis_manibus, LIRE_3CAD$form_dis_manibus, method= "dl")
table(dl_distance_3CAD)
dl_distance_3CAD


# renaming rows and columns
idnames <- unique(as.character(LIRE_3CAD$id))
rownames(dl_distance_3CAD) <- idnames
colnames(dl_distance_3CAD) <- idnames

# Clustering the distance results in a dendrogram
hc_3CAD <- hclust(as.dist(dl_distance_3CAD), method = "complete")

plot(hc_3CAD, main ="Clustering of 'Dis Manibus' inscriptions in the 3rd c. AD", xlab="Clusters")
rect.hclust(hc_3CAD, k=3)
```


## Three networks in time

https://yulab-smu.top/treedata-book/chapter4.html
```{r}
# convert 'hclust' to 'phylo' object
phylo_tree <- as.phylo(hc_1CAD)

# get edges
graph_edges <- phylo_tree$edge

# get graph from edge list
graph_net <- graph.edgelist(graph_edges)

# plot graph
plot(graph_net)
```


```{r}
dl_distance_1CADdf<- as.data.frame(dl_distance_1CAD)
dl_distance_2CADdf<- as.data.frame(dl_distance_2CAD)
dl_distance_3CADdf<- as.data.frame(dl_distance_3CAD)
```

```{r, fig.width=30}
dl_distance_1CADdf[1:3,1:3]

library(igraph)

network1 <- graph_from_incidence_matrix(dl_distance_1CADdf, weighted=TRUE)
plot(network1)




```
```{r}
network2 <- graph_from_incidence_matrix(dl_distance_2CADdf, weighted=TRUE)
plot(network2)

```

```{r}
network3 <- graph_from_incidence_matrix(dl_distance_3CADdf, weighted=TRUE)
plot(network3)
```



