---
title: "Mapping Network Measures on Inscription-Rich places Through Time"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries

```{r libraries, include=FALSE}
library(raster)
library(rgeos)
library(sf)
library(tidyverse)
# library(htmltools)
# library(googlesheets4)
library(mapview)
```


# Task 1: Get spatial data for Roman Provinces


```{r load-province-data}
provinces <- st_read("https://raw.githubusercontent.com/pelagios/magis-pleiades-regions/main/pleiades-regions-magis-pelagios.geojson")
plot(provinces$geometry)
provinces

```

# Task 2: Get spatial data for network


```{r load-network-data}
#
```

# Task 3: Get cities with inscriptions and make long and spatial

```{r load-city-data}
cities <- read_csv("../scripts_sf/data/orbis_nodes_enriched.csv")

cities <- cities %>% 
  st_as_sf(coords = c("y", "x"), crs = 4326)

cities_l <- pivot_longer(data=cities, 
                         cols=c(LIRE_per1_N, LIRE_per2_N, LIRE_per3_N),
                         names_to = "century",
                         values_to = "InscriptionNo" )

cities_g <- cities_l %>% 
  st_as_sf(coords = c("y", "x"), crs = 4326)
cities_g
plot(provinces$geometry);plot(cities_g$geometry, add=TRUE)  
```

# Task 4: Make a neat map of cities with inscription numbers over time
```{r view-flats, fig.width = 12}
library(tmap)
tmap_options(limits = c(facets.view = 3)) # we want to view 5 periods
tmap_mode(mode = "view" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g) +
  tm_facets(by = "century",
            ncol=1, nrow = 3)+
  tm_symbols(size = "InscriptionNo", col = "darkblue",
             scale = 4,
             title.size = "number of inscriptions")+
  tm_layout(main.title = "Nodes by inscription numbers",
            legend.outside = TRUE)
```

# Pridej k hornim facetkam degree, betweenness, and gravity 

# Task 5: Map betweenness and gravity values on the network
```{r measures}
# Get cities with the 20 highest degree values
top_20_deg <- cities %>% 
  filter(degree%in%head(sort(cities$degree,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_deg <- head(top_20_deg$X1,20)

top_20_bb <- cities %>% 
  filter(bb%in%head(sort(cities$bb,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_bb <- head(top_20_bb$X1,20)

top_20_bb_gravity <- cities %>% 
  filter(bb_gravity%in%head(sort(cities$bb_gravity,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_bb_gravity <- head(top_20_bb_gravity$X1,20)

top_20_bb_expense <- cities %>% 
  filter(bb_expense %in% head(sort(cities$bb_expense,decreasing = TRUE), 20)) %>%   select(X1) %>% 
  head(20)
top_20_bb_expense <- head(top_20_bb_expense$X1,20)

# Pull cities with over 100 inscriptions per century
head(sort(cities$LIRE_per3_N,decreasing = TRUE), 150)
Lire_1 <- cities$X1[which(cities$LIRE_per1_N > 100)]
Lire_2 <- cities$X1[which(cities$LIRE_per2_N > 100)]
Lire_3 <- cities$X1[which(cities$LIRE_per3_N > 100)]
```


# Visualisations - 0-100 AD
```{r inscription-count}
library(mapview)
mapviewOptions(viewer.suppress = FALSE) 
cities_g
cities_g %>% 
  filter(X1%in%top_20) %>% 
  plot()


library(tmap)
#tmap_options(limits = c(facets.view = 3)) # we want to view 5 periods
tmap_mode(mode = "plot" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_deg,]) +  # highest 20 degree values
  tm_symbols(size = "degree",
             col = "blue",
             scale = 2,
              title.size = "Degree centrality")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "Cities (in red) with over 100 inscriptions in AD 0-100")
```

```{r 100-AD-betweenness}
tmap_mode(mode = "plot" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 2,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "Cities (in red) with over 100 inscriptions in AD 0-100")

```
# Gravity
```{r gravity}
tmap_mode(mode = "plot" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_gravity,]) +  # highest 20 degree values
  tm_symbols(size = "bb_gravity",
             col = "purple",
             scale = 1,
              title.size = "Betweenness gravity")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "Cities (in red) with over 100 inscriptions in AD 0-100")
```
# Expense

```{r expense}
tmap_mode(mode = "plot" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_expense,]) +  # highest 20 degree values
  tm_symbols(size = "bb_expense",
             col = "green",
             scale = 1.5,
              title.size = "Betweenness expense")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "Cities (in red) with over 100 inscriptions in AD 0-100")
```


# 100 - 200 AD 
```{r centrality-degree}
#library(tmap)
#tmap_options(limits = c(facets.view = 3)) # we want to view 5 periods
tmap_mode(mode = "plot" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_deg,]) +  # highest 20 degree values
  tm_symbols(id ="degree", 
             size = 2, 
             col = "red",
             title.size = "highest-degree nodes")+
  tm_layout(main.title = "Centrality degree")
```

```{r highest-inscriptions-per-century}
# Get cities with the highest number of inscriptions 
top_20i <- cities %>% 
  filter(LIRE_per1_N%in%head(sort(cities$LIRE_per1_N,decreasing = TRUE), 20)) %>%   select(X1) %>% 
  head(20)
top_20i <- head(top_20i$X1,20)
```

