---
title: "Mapping Network Measures on Inscription-Rich places Through Time"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Libraries

```{r libraries, include=FALSE}
library(raster)
library(rgeos)
library(sf)
library(tidyverse)
# library(htmltools)
# library(googlesheets4)
library(mapview)
```


# Task 1: Get spatial data for Roman Provinces


```{r load-province-data}
provinces <- st_read("https://raw.githubusercontent.com/pelagios/magis-pleiades-regions/main/pleiades-regions-magis-pelagios.geojson")
plot(provinces$geometry)
provinces

```

# Task 2: Get spatial data for network


```{r load-network-data, eval = false}
# library(sdam)
# library(jsonlite)
# library(getPass)
# user <-  "616760@au.dk"
# resp = request("orbis_nodes_enriched.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/urban", method="GET", cred=c(user, getPass("your sciencedata password: ")))
# 
# list_json <- jsonlite::fromJSON(resp)
# orbis_nodes = as_tibble(list_json)
# head(orbis_nodes) # does not look well, no time to fix, downloaded file manually
```


# Task 3: Get cities with inscriptions and make long and spatial
```{r load-city-data}
cities <- read_csv("data/orbis_nodes_enriched.csv")


cities_l <- pivot_longer(data=cities, 
                         cols=c(LIRE_per0_N,
                                LIRE_per1_N, 
                                LIRE_per2_N, 
                                LIRE_per3_N,
                                LIRE_per4_N),
                         names_to = "century",
                         values_to = "InscriptionNo" )
cities <- cities %>% 
  st_as_sf(coords = c("y", "x"), crs = 4326)
cities_g <- cities_l %>% 
  st_as_sf(coords = c("y", "x"), crs = 4326)
cities
cities_g
plot(provinces$geometry);plot(cities$geometry, add=TRUE)  
?list()
?replace_na()
```

# Task 4a: Make a neat map of cities with inscription numbers over time
```{r view-flats, fig.width = 12}
library(tmap)
tmap_options(limits = c(facets.view = 5)) # we want to view 5 periods
tmap_mode(mode = "view" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g) +
  tm_facets(by = "century",
            ncol=1, nrow = 3)+
  tm_symbols(size = "InscriptionNo", col = "darkblue",
             scale = 4,
             title.size = "number of inscriptions")+
  tm_layout(main.title = "Nodes by inscription numbers",
            legend.outside = TRUE)
```


# Task 4b: Make a neat map of cities with inscription numbers over time per 1000 inhabitants
```{r view-flats, fig.width = 12}
cities_g$insc_per_1000pax <- cities_g$InscriptionNo/cities_g$pop_est
library(tmap)
tmap_options(limits = c(facets.view = 5)) # we want to view 5 periods
tmap_mode(mode = "view" )
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g) +
  tm_facets(by = "century",
            ncol=1, nrow = 3)+
  tm_symbols(size = "insc_per_1000pax", col = "darkblue",
             scale = 4,
             title.size = "inscription count per 1000 inhabitants") +
  tm_layout(main.title = "Nodes by inscription numbers",
            legend.outside = TRUE)
```
# Pridej k hornim facetkam degree, betweenness, and gravity 

# Task 5: Map betweenness and gravity values on the network
```{r measures}
# Get cities with the 20 highest degree values
top_20_deg <- cities %>% 
  filter(degree%in%head(sort(cities$degree,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_deg <- head(top_20_deg$X1,20)

top_20_bb <- cities %>% 
  filter(bb%in%head(sort(cities$bb,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_bb <- head(top_20_bb$X1,20)

top_20_bb_gravity <- cities %>% 
  filter(bb_gravity%in%head(sort(cities$bb_gravity,decreasing = TRUE), 20)) %>% 
  select(X1) %>% 
  head(20)
top_20_bb_gravity <- head(top_20_bb_gravity$X1,20)

top_20_bb_expense <- cities %>% 
  filter(bb_expense %in% head(sort(cities$bb_expense,decreasing = TRUE), 20)) %>%   select(X1) %>% 
  head(20)
top_20_bb_expense <- head(top_20_bb_expense$X1,20)

# Pull cities with over 100 inscriptions per century
head(sort(cities$LIRE_per3_N,decreasing = TRUE), 150)
Lire_1 <- cities$X1[which(cities$LIRE_per1_N > 100)]
Lire_2 <- cities$X1[which(cities$LIRE_per2_N > 100)]
Lire_3 <- cities$X1[which(cities$LIRE_per3_N > 100)]
```


## Visualisations - 0-100 AD Centrality
```{r inscription-count-degree-centrality}
library(mapview)
mapviewOptions(viewer.suppress = FALSE) 
cities_g
cities_g %>% 
  filter(X1 %in% top_20_deg) %>% 
  mapview()


library(tmap)
#tmap_options(limits = c(facets.view = 3)) # we want to view 5 periods
tmap_mode(mode = "plot" )

degree_100 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_deg,]) +  # highest 20 degree values
  tm_symbols(size = "degree",
             col = "blue",
             scale = 1,
              title.size = "Degree centrality")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD0-100: cities with >100 inscriptions",
            legend.outside = TRUE)
```

## Betweenness
```{r 100-AD-betweenness}
bb_100 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD0-100: cities with >100 inscriptions",
            legend.outside = TRUE)
bb_100
```
## Gravity
```{r gravity}
gravity_100 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_gravity,]) +  # highest 20 degree values
  tm_symbols(size = "bb_gravity",
             col = "purple",
             scale = 1,
              title.size = "Betweenness gravity")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD0-100: cities with >100 inscriptions",
            legend.outside = TRUE)
```
## Expense

```{r expense}
tmap_mode(mode = "plot" )

expense_100 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_expense,]) +  # highest 20 degree values
  tm_symbols(size = "bb_expense",
             col = "green",
             scale = 1.5,
              title.size = "Betweenness expense")+
tm_shape(cities[cities$X1 %in% Lire_1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per1_N", 
             size = "LIRE_per1_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD0-100: cities with >100 inscriptions",
            legend.outside = TRUE)
```

## Visualisations - 100-200 AD Centrality
```{r 200-AD-centrality-degree}

degree_200 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_deg,]) +  # highest 20 degree values
  tm_symbols(size = "degree",
             col = "blue",
             scale = 1,
              title.size = "Degree centrality")+
tm_shape(cities[cities$X1 %in% Lire_2,]) +  # most inscriptionsin 32 AD
  tm_symbols(id ="LIRE_per2_N", 
             size = "LIRE_per2_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD100-200: Cities with >100 inscriptions",
            legend.outside = TRUE)
```

## Betweenness
```{r betweenness-200}
tmap_mode(mode = "plot" )

bb_200 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_2,]) +  # most inscriptionsin 2c AD
  tm_symbols(id ="LIRE_per2_N", 
             size = "LIRE_per2_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD100-200: Cities with >100 inscriptions",
            legend.outside = TRUE)

```


## Gravity
```{r gravity-200}
tmap_mode(mode = "plot" )

gravity_200 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_gravity,]) +  # highest 20 degree values
  tm_symbols(size = "bb_gravity",
             col = "purple",
             scale = 1,
              title.size = "Betweenness gravity")+
tm_shape(cities[cities$X1 %in% Lire_2,]) +  # most inscriptionsin 2c AD
  tm_symbols(id ="LIRE_per2_N", 
             size = "LIRE_per2_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD100-200: Cities with >100 inscriptions",
            legend.outside = TRUE)
```
## Expense 2nd century

```{r expense-200}
tmap_mode(mode = "plot" )

expense_200 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_expense,]) +  # highest 20 degree values
  tm_symbols(size = "bb_expense",
             col = "green",
             scale = 1.5,
              title.size = "Betweenness expense")+
tm_shape(cities[cities$X1 %in% Lire_2,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per2_N", 
             size = "LIRE_per2_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD100-200: Cities with >100 inscriptions",
            legend.outside = TRUE)
```


## Visualisations - 200-300 AD
```{r centrality-degree-300}
degree_300 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_deg,]) +  # highest 20 degree values
  tm_symbols(size = "degree",
             col = "blue",
             scale = 1,
              title.size = "Degree centrality")+
tm_shape(cities[cities$X1 %in% Lire_3,]) +  # most inscriptions in 3c AD
  tm_symbols(id ="LIRE_per3_N", 
             size = "LIRE_per3_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD200-300: Cities with >100 inscriptions",
            legend.outside = TRUE)
```

```{r betweenness-300}
bb_300 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_3,]) +  # most inscriptions in 3c AD
  tm_symbols(id ="LIRE_per3_N", 
             size = "LIRE_per3_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD200-300: Cities with >100 inscriptions",
            legend.outside = TRUE)
```

```{r betw3eenness-gravity-300}
tmap_mode(mode = "plot" )

gravity_300 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_gravity,]) +  # highest 20 degree values
  tm_symbols(size = "bb_gravity",
             col = "purple",
             scale = 1,
              title.size = "Betweenness gravity")+
tm_shape(cities[cities$X1 %in% Lire_3,]) +  # most inscriptions in 3c AD
  tm_symbols(id ="LIRE_per3_N", 
             size = "LIRE_per3_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD200-300: Cities with >100 inscriptions",
            legend.outside = TRUE)
```

```{r betweenness-expense-300}
tmap_mode(mode = "plot" )

expense_300 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb_expense,]) +  # highest 20 degree values
  tm_symbols(size = "bb_expense",
             col = "green",
             scale = 1.5,
              title.size = "Betweenness expense")+
tm_shape(cities[cities$X1 %in% Lire_3,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="LIRE_per3_N", 
             size = "LIRE_per3_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(#main.title = "AD200-300: Cities with >100 inscriptions",
            legend.outside = TRUE)
```
# Summary AD 0 - 100
```{r}
current.mode <- tmap_mode("plot")
tmap_arrange(degree_100, bb_100, gravity_100, expense_100, asp = NA)
tmap_mode(current.mode)
```
# Summary AD 100 - 200
```{r}
current.mode <- tmap_mode("plot")
tmap_arrange(degree_200, bb_200, gravity_200, expense_200, asp = NA)
tmap_mode(current.mode)
```
# Summary AD 200 - 300
```{r}
current.mode <- tmap_mode("plot")
tmap_arrange(degree_300, bb_300, gravity_300, expense_300, asp = NA)
tmap_mode(current.mode)
```


# Task 6: Map increase in production over time


```{r increase}
Lire_increase1 <- cities$X1[which(cities$LIRE_per1_N>cities$LIRE_per0_N)]
Lire_increase2 <- cities$X1[which(cities$LIRE_per2_N>cities$LIRE_per1_N)]
Lire_increase3 <- cities$X1[which(cities$LIRE_per3_N>cities$LIRE_per2_N)]
Lire_increase4 <- cities$X1[which(cities$LIRE_per4_N>cities$LIRE_per3_N)]
cities$increase1 <- cities$LIRE_per1_N-cities$LIRE_per0_N
cities$increase2 <- cities$LIRE_per2_N-cities$LIRE_per1_N
cities$increase3 <- cities$LIRE_per3_N-cities$LIRE_per2_N
cities$increase4 <- cities$LIRE_per4_N-cities$LIRE_per3_N

```

## -50BC - AD100
```{r 1st-c}
tmap_mode("plot")
increase_100 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_increase1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id = "increase1", 
             size = "increase1", 
             col = "red",
             scale = 4,
             title.size = "Additional inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "50BC -AD100: increase over previous period",
            legend.outside = TRUE)
increase_100
```


## 100-200
```{r 200AD-incrase-vs-betweenness}
tmap_mode("plot")
increase_200 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_increase2,]) +  # most inscriptionsin 1c AD
  tm_symbols(id = "increase2", 
             size = "increase2", 
             col = "red",
             scale = 4,
             title.size = "Additional inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "AD100-200: increase over previous period",
            legend.outside = TRUE)
increase_200

```
## AD200-300
```{r 300AD-increase-vs-betweenness}
tmap_mode("plot")
#tmap_mode("view")
increase_300 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_increase3,]) +  # most inscriptionsin 1c AD
  tm_symbols(id = "incrase3",
             size = "increase3", 
             col = "red",
             scale = 4,
             title.size = "Additional inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "AD200-300: increase over previous period",
            legend.outside = TRUE)
increase_300
```

## AD300-350
```{r 350AD-increase-vs-betweenness}
tmap_mode("plot")
increase_350 <- tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_increase4,]) +  # most inscriptionsin 1c AD
  tm_symbols(id = "increase4", 
             size = "increase4", 
             col = "red",
             scale = 4,
             title.size = "Additional inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "AD300-350: increase over previous period",
            legend.outside = TRUE)
increase_350
```

## Summary of growth and Betweenness AD 0 - 350
```{r}
current.mode <- tmap_mode("plot")
tmap_arrange(increase_100, increase_200,increase_300, increase_350, asp = NA)
tmap_mode(current.mode)
```

Next steps:
1. make animation
2. Select the nearest node to a given site with 100+ inscriptions in given century 
Tabulate the measures for the proximate node -- correlation with what NA properties? 

3.Select Judea in 2nd c, Dacia in 3rd c 

# Task 7: Map increase in production per 1000 residents over time

How many inscriptions per 1000 people in an urban area?
```{r}
cities$increase1ppax <- (cities$LIRE_per1_N-cities$LIRE_per0_N)/(cities$pop_est/1000)
hist(cities$increase1ppax)
cities$increase2ppax <- (cities$LIRE_per2_N-cities$LIRE_per1_N)/(cities$pop_est/1000)
cities$increase3ppax <- (cities$LIRE_per3_N-cities$LIRE_per2_N)/(cities$pop_est/1000)
cities$increase4ppax <- (cities$LIRE_per4_N-cities$LIRE_per3_N)/(cities$pop_est/1000)
```

## Change in production per century per 1000 inhabitants 
```{r}
tmap_mode("plot")
inscr_attribute <- "increase1ppax"
tm_shape(provinces) +
  tm_polygons(col="cornsilk2", border.alpha = 0) +
tm_shape(cities_g[cities_g$X1 %in% top_20_bb,]) +  # highest 20 degree values
  tm_symbols(size = "bb",
             col = "darkred",
             scale = 1,
              title.size = "Betweenness centrality")+
tm_shape(cities[cities$X1 %in% Lire_increase1,]) +  # most inscriptionsin 1c AD
  tm_symbols(id = inscr_attribute, 
             size = inscr_attribute, 
             col = "red",
             scale = 3,
             title.size = "Additional inscriptions",
             alpha = 0.7)+
  tm_layout(main.title = "Increase per 1000 residents",
            legend.outside = TRUE)

```

## Doublecheck cities


```{r}
colnames(cities)
library(DT)
cities %>%
  st_drop_geometry() %>% 
  select(label, pop_est, LIRE_per1_N, increase1, increase1ppax) %>% 
  filter(label == "Roma" | label == "Pompeii" |label == "Aquincum") %>% 
  arrange(desc(pop_est)) %>% 
  datatable()
```
## Overview of change over time with population held static 
```{r}

```


# LIRE inscriptions

```{r}
colnames(provinces)
sort(provinces$name)

library(sf)

lire <- st_read("data/LIREg.geojson")
lire_sm <- lire %>% 
  #filter(province == "Iudaea" | province == "Dacia") %>% 
  select(EDH.ID, EDCS.ID, type_of_inscription_auto, province_label_clean, country_clean, clean_text_interpretive_word_EDCS, not_after, not_before)

hist(lire_sm$not_before) # postquem
hist(lire_sm$not_after) #antequem


# Single province - Judea
lire_sm%>% 
 # filter(province_label_clean == "Iudaea")  %>% 
   filter(province_label_clean == "Palestina")  %>% 
 # filter(province_label_clean == "Dacia") %>% 
  filter(not_before >= 100 ) %>% 
  select(province_label_clean, type_of_inscription_auto) %>% 
  group_by(province_label_clean, type_of_inscription_auto) %>% 
  #count()
  summarize(n=n()) %>% 
  arrange(desc(n))

lire_sm%>% 
  #filter(province_label_clean == "Iudaea")  %>% 
  #filter(province_label_clean == "Dacia") %>% 
  #filter(province_label_clean == "Africa Proconsularis") %>%
  filter(province_label_clean == "Latium et Campania (Regio I)" |province_label_clean == "Roma" ) %>% 
  filter(not_after <= 400 ) %>% 
  select(province_label_clean, type_of_inscription_auto) %>% 
  group_by(province_label_clean, type_of_inscription_auto) %>% 
  #count()
  summarize(n=n()) %>% 
  arrange(desc(n))

sort(unique(lire_sm$province_label_clean))

plot(lire_sm$geometry)

library(tmap)
tmap_mode(mode = "view" )
tm_shape(provinces) +
  tm_polygons(col = "cornsilk2", border.alpha = 0) +
tm_shape(cities[cities$X1 %in% Lire_2,]) +  # most inscriptionsin 1c AD
  tm_symbols(id ="label", 
             size = "LIRE_per2_N", 
             col = "red",
             scale = 3,
             title.size = "Number of inscriptions",
             alpha = 0.5)+
  tm_layout(main.title = "AD0-100: cities with >100 inscriptions",
            legend.outside = TRUE)
# tm_shape(lire_sm) +
#   tm_symbols(id  = "province_label_clean")
  
```



# Correlation
```{r}
nodes <- cities %>% 
  st_drop_geometry() %>% 
  select(label, pop_est:degree,increase1ppax:increase4)
result <- cor(x = nodes[,-1], method = "spearman")
result[1,] # correlation of population to everything else
result[8,] # correlation of betweenness centrality measure to everything else
result[12,] # eigenvector (influence of a node in a network on the basis of expense / geodesic distance between pair of actors) does not matter in Pearson, but impacts total production in spearman model
result[13,] # degree
# katz assigns influence on the basis of  first and second degree neighbors connecting through immediate neighbors

```

